Inspiring Confidence and Easing Insecurity in the Pre-election period: The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections

### 2025-03-19 docs/_tex/index.tex
reformated tables in appendix

% ---------------------------
% END CUSTOM PREAMBLE STUFF
% ---------------------------
\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\usepackage{rotating}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{dcolumn}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\centering\begingroup\fontsize{9}{11}\selectfont

\begin{tabular}{lcccc}
\toprule
\textbf{Demographic} & \textbf{N} & \makecell[c]{\textbf{Overall}\ \ \\N = 1,287} & \makecell[c]{\textbf{Control}\ \ \\N = 637} & \makecell[c]{\textbf{Treatment}\ \ \\N = 650}\\
\midrule
\textbf{Age group} & 1,287 &  &  & \\
\hspace{1em}18-34 &  & 350 (27\%) & 170 (27\%) & 180 (28\%)\\
\hspace{1em}35-54 &  & 480 (37\%) & 245 (38\%) & 235 (36\%)\\
\hspace{1em}55-74 &  & 390 (30\%) & 198 (31\%) & 192 (30\%)\\
\hspace{1em}75-85+ &  & 67 (5.2\%) & 24 (3.8\%) & 43 (6.6\%)\\
\addlinespace
\textbf{Gender} & 1,272 &  &  & \\
\hspace{1em}Male &  & 598 (47\%) & 289 (46\%) & 309 (48\%)\\
\hspace{1em}Female &  & 658 (52\%) & 330 (52\%) & 328 (51\%)\\
\hspace{1em}Other/Refused &  & 16 (1.3\%) & 10 (1.6\%) & 6 (0.9\%)\\
\hspace{1em}NA &  & 15 & 8 & \vphantom{4} 7\\
\addlinespace
\textbf{Race/Ethnicity} & 1,272 &  &  & \\
\hspace{1em}White &  & 975 (77\%) & 478 (76\%) & 497 \vphantom{1} (77\%)\\
\hspace{1em}Asian &  & 51 (4.0\%) & 25 (4.0\%) & 26 (4.0\%)\\
\hspace{1em}Black &  & 164 (13\%) & 85 (14\%) & 79 (12\%)\\
\hspace{1em}Other &  & 24 (1.9\%) & 12 (1.9\%) & 12 (1.9\%)\\
\addlinespace
\hspace{1em}Hispanic &  & 44 (3.5\%) & 24 (3.8\%) & 20 (3.1\%)\\
\hspace{1em}American Indian &  & 14 (1.1\%) & 5 (0.8\%) & 9 (1.4\%)\\
\hspace{1em}NA &  & 15 & 8 & \vphantom{3} 7\\
\textbf{White or Non-White} & 1,272 &  &  & \\
\hspace{1em}Non-White &  & 297 (23\%) & 151 (24\%) & 146 (23\%)\\
\addlinespace
\hspace{1em}White &  & 975 (77\%) & 478 (76\%) & 497 (77\%)\\
\hspace{1em}NA &  & 15 & 8 & \vphantom{2} 7\\
\textbf{Education} & 1,272 &  &  & \\
\hspace{1em}H.S. or less &  & 362 (28\%) & 174 (28\%) & 188 (29\%)\\
\hspace{1em}Some college no degree &  & 283 (22\%) & 142 (23\%) & 141 (22\%)\\
\addlinespace
\hspace{1em}College degree &  & 461 (36\%) & 236 (38\%) & 225 (35\%)\\
\hspace{1em}Postgraduate degree &  & 166 (13\%) & 77 (12\%) & 89 (14\%)\\
\hspace{1em}NA &  & 15 & 8 & \vphantom{1} 7\\
\textbf{Party ID} & 1,268 &  &  & \\
\hspace{1em}Independent &  & 162 (13\%) & 83 (13\%) & 79 (12\%)\\
\addlinespace
\hspace{1em}Republican &  & 540 (43\%) & 262 (42\%) & 278 (43\%)\\
\hspace{1em}Democrat &  & 566 (45\%) & 283 (45\%) & 283 (44\%)\\
\hspace{1em}NA &  & 19 & 9 & 10\\
\textbf{Military Relation} & 1,272 &  &  & \\
\hspace{1em}No relation &  & 789 (62\%) & 394 (63\%) & 395 (61\%)\\
\addlinespace
\hspace{1em}Only family &  & 362 (28\%) & 182 (29\%) & 180 (28\%)\\
\hspace{1em}Served w/fam &  & 64 (5.0\%) & 31 (4.9\%) & 33 (5.1\%)\\
\hspace{1em}Served &  & 57 (4.5\%) & 22 (3.5\%) & 35 (5.4\%)\\
\hspace{1em}NA &  & 15 & 8 & 7\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\multicolumn{5}{l}{\textsuperscript{a} Independents do not identify nor 'lean' toward either political party}\\
\end{tabular}
\endgroup{}

>>>>

% ---------------------------
% END CUSTOM PREAMBLE STUFF
% ---------------------------
\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\usepackage{rotating}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\usepackage{dcolumn}
\usepackage{etoolbox}
\AtBeginEnvironment{longtblr}{\begin{singlespacing}}
\AtEndEnvironment{longtblr}{\end{singlespacing}}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]Q[]},
column{1,2,3,4}={}{font=\fontsize{0.7em}{1em}\selectfont,},
rowsep={0.1em}, colsep = {0.5em},
}                     %% tabularray inner close
\toprule
\textbf{Demographic} & \textbf{Overall (N = 1287)} & \textbf{Control (N = 637)} & \textbf{Treatment (N = 650)} \\
\textbf{Age group} &  &  &  \\
18-34 & 350 (27\%) & 170 (27\%) & 180 (28\%) \\
35-54 & 480 (37\%) & 245 (38\%) & 235 (36\%) \\
55-74 & 390 (30\%) & 198 (31\%) & 192 (30\%) \\
75-85+ & 67 (5.2\%) & 24 (3.8\%) & 43 (6.6\%) \\
\textbf{Gender} &  &  &  \\
Male & 598 (47\%) & 289 (46\%) & 309 (48\%) \\
Female & 658 (52\%) & 330 (52\%) & 328 (51\%) \\
Other/Refused & 16 (1.3\%) & 10 (1.6\%) & 6 (0.9\%) \\
NA & 15 & 8 & 7 \\
\textbf{Race/Ethnicity} &  &  &  \\
White & 975 (77\%) & 478 (76\%) & 497 (77\%) \\
Asian & 51 (4.0\%) & 25 (4.0\%) & 26 (4.0\%) \\
Black & 164 (13\%) & 85 (14\%) & 79 (12\%) \\
Other & 24 (1.9\%) & 12 (1.9\%) & 12 (1.9\%) \\
Hispanic & 44 (3.5\%) & 24 (3.8\%) & 20 (3.1\%) \\
American Indian & 14 (1.1\%) & 5 (0.8\%) & 9 (1.4\%) \\
NA & 15 & 8 & 7 \\
\textbf{Education} &  &  &  \\
H.S. or less & 362 (28\%) & 174 (28\%) & 188 (29\%) \\
Some college no degree & 283 (22\%) & 142 (23\%) & 141 (22\%) \\
College degree & 461 (36\%) & 236 (38\%) & 225 (35\%) \\
Postgraduate degree & 166 (13\%) & 77 (12\%) & 89 (14\%) \\
NA & 15 & 8 & 7 \\
\textbf{Party ID} &  &  &  \\
Independent & 162 (13\%) & 83 (13\%) & 79 (12\%) \\
Republican & 540 (43\%) & 262 (42\%) & 278 (43\%) \\
Democrat & 566 (45\%) & 283 (45\%) & 283 (44\%) \\
NA & 19 & 9 & 10 \\
\bottomrule
\end{tblr}

### 2025-03-19 index.qmd
reformated tables in appendix

# load packages
library(tidyverse)
library(modelsummary)
library(tinytable) # simple tables in html, LaTeX, markdown, word, pdf, typst
library(ordinal)
library(marginaleffects)
library(easystats)
library(patchwork)

@@

::: {.content-visible when-format="bookup-html" unless-format="pdf"}

@@

::: {.content-visible when-format="pdf" unless-format="bookup-html"}

@@

```{r}
#| label: tbl-demog
#| tbl-cap: "Sample Demographics"
#| tbl-pos: 'H'

# descriptive stats of categorical variables
# best method for html document
tbl.desc <- data |>  
  labelled::set_variable_labels(
    age_4cat = "Age group",
    gender_3cat = "Gender",
    race2 = "Race/Ethnicity",
    race_wnw = "White or Non-White",
    educ_4cat = "Education",
    partyid_3cat = "Party ID",
    milrelation  = "Military Relation"
  ) |> 
  gtsummary::tbl_summary(
    by = group,
    include = c(
    age_4cat, 
    gender_3cat, 
    race2,
    race_wnw,
    educ_4cat, 
    partyid_3cat,
    milrelation),
    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
    missing = "ifany",
    missing_text = "NA") |> 
  gtsummary::add_n() |> 
  gtsummary::add_overall() |> 
  gtsummary::modify_header(label = "**Demographic**") |> 
  gtsummary::bold_labels()

gtsummary::as_kable_extra(tbl.desc, booktabs = T) |>
  kableExtra::add_footnote(
    label = "Independents do not identify nor 'lean' toward either political party") |> 
  kableExtra::kable_styling(
    font_size = 9, 
    protect_latex = T)

# gtsummary::as_gt(tbl.desc) |>  
#   gt::tab_footnote(
#     footnote = "Independents do not identify nor 'lean' toward either political party",
#     placement = "left"
#     ) |>  
#   gt::cols_align(align = 'left', columns = everything()) |> 
#   gt::tab_options(
#     table.font.size = "small",
#     data_row.padding = gt::px(1)
#   )

>>>>

# load packages
library(tidyverse)
library(modelsummary)
library(tinytable) # simple tables in html, LaTeX, markdown, word, pdf, typst
library(litedown)
library(ordinal)
library(marginaleffects)
library(easystats)
library(patchwork)

@@

::: {.content-visible when-format="html" unless-format="pdf"}

@@

::: {.content-visible when-format="pdf" unless-format="html"}

@@

```{r}
#| label: sample-desc-setup
#| tbl-cap: "Sample Demographics"
#| tbl-pos: 'H'

gtsummary::theme_gtsummary_compact()

# descriptive stats of categorical variables
# best method for html document
tbl.desc <- data |>  
  labelled::set_variable_labels(
    age_4cat = "Age group",
    gender_3cat = "Gender",
    race2 = "Race/Ethnicity",
    educ_4cat = "Education",
    partyid_3cat = "Party ID"
  ) |> 
  gtsummary::tbl_summary(
    by = group,
    include = c(
    age_4cat, 
    gender_3cat, 
    race2,
    educ_4cat, 
    partyid_3cat),
    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
    missing = "ifany",
    missing_text = "NA") |> 
  gtsummary::add_n() |> 
  gtsummary::add_overall() |> 
  gtsummary::modify_header(label = "**Demographic**") |> 
  gtsummary::bold_labels()

```{r}
#| label: tbl-demog
#| tbl-cap: "Sample Demographics"
#| tbl-colwidths: 80
#| tbl-pos: 'H'

tbl.desc |> 
  gtsummary::as_tibble() |> 
  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
                "**Control (N = 637)**" = "**Control**  \nN = 637",
                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
  dplyr::select(-"**N**") |> 
  tinytable::tt(theme = "spacing") |> 
  tinytable::format_tt(markdown = T) |> 
  tinytable::format_tt(replace = " ") |> 
  tinytable::style_tt(fontsize = 0.70)
